Real-world Feasibility Analysis of ACT Algorithm for Robotic Manipulation on Home

### 2025-05-03 paper.tex
feat: 添加表格 Transformer 层架构的输入/输出维度

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}
%
\usepackage[T1]{fontenc}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{adjustbox}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{array} 
\usepackage{float}
\usepackage{multirow}
\usepackage{subcaption}
\usepackage{tabularx} % 在导言区添加此宏包
\usepackage{booktabs}  % 专业表格线
\usepackage{caption}   % 标题控制

@@

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}
%
\usepackage[T1]{fontenc}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{adjustbox}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{array} 
\usepackage{float}
\usepackage{multirow}
\usepackage{subcaption}
\usepackage{tabularx} % 在导言区添加此宏包
\usepackage{booktabs}  % 专业表格线
\usepackage{array}     % 提供更好的列格式控制

\usepackage{caption}   % 标题控制

@@

The dimensional information of key components is presented in \textbf{\cref{tab:dim_summary}} to clarify the model pipeline. The architecture follows a standard visual encoding and sequence modeling design: image features are first extracted and flattened, then fused with proprioceptive state and latent variables, and finally decoded into a sequence of predicted joint actions.

\begin{table}[htbp]
	\centering
	\caption{Dimensions of CVAE policy network modules}
	\label{tab:dim_summary}
	\begin{tabularx}{\textwidth}{@{}>{\raggedright\arraybackslash}X >{\raggedright\arraybackslash}X >{\raggedright\arraybackslash}X >{\raggedright\arraybackslash}X@{}}
		\toprule
		\textbf{Module} & \textbf{Input Dim} & \textbf{Output Dim} & \textbf{Function} \\
		\midrule
		CNN & $4 \times 480 \times 640 \times 3$ & $1200 \times 512$ & Visual feature extraction \\
		Encoder & $1202 \times 512$ & $1202 \times 512$ & Fuse image, joints and latent $z$ \\
		Decoder & $k \times 512$ & $k \times 14$ & Generate $k$-step action sequence \\
		\bottomrule
	\end{tabularx}
\end{table}
